Regression Models Course Project
================================

Summary
-------

According to dataset mtcars we made analysis toanswer questions:

* “Is an automatic or manual transmission better for MPG”
* "Quantify the MPG difference between automatic and manual transmissions"

and statistically cars with manual transmission has higher MPG that cars with automatic.
In the second part of project we find the best combinations of variables ```mpg ~ wt + qsec +am```


Automatic amd manual transmission
---------------------------------

Loading data:
```{r}
library(datasets)
data(mtcars)
```
Boxplot illustrates relationship between manual and automatioc transmissions:
```{r}
boxplot(mpg~am, data=mtcars, ylab='MPG', xlab='Type of transmission' )
```

Mean of mechanical transmission higher than mean of automatical transmission. Create t-test to prove it.

```{r}
t.test(mpg~am, data=mtcars)
```

So we reject null-hypotesis and we know that type of transmission is important. Now we shoul create a model to describe it.


First we create a basic regerssion model
```{r}
basic_model <- lm(mpg~am, data=mtcars)
```
Then create a "best" model

```{r results='hide'}
best_model <- step(lm(data=mtcars, mpg~.))
```

```{r}
summary(best_model)
```
And compare both
```{r}
anova(basic_model, best_model)
```

Our "best model" is really better than general. Now we shouldcheckout normality of our residuals. So we can use q-q plot for this:

```{r}
par(mfrow=c(2,2))
plot(best_model)
```
